DENSITY AND SPECIFIC GRAVITY
1. How would you find without the use of balances the weight of a wooden ball which, when placed in a tumbler full of water, causes an overflow of 1 00 c.c.?
2. A piece of aluminum weighs 200 g. in air and 100 g. in water, (\emph{a}) What is its density in the French system? (\emph{b}) in the English system? (\emph{c}) its sp. gr. in the French system? (\emph{d}) in the English system?
3. What will be the volume of 280 g. of substance of sp. gr. 14?
4. A given substance weighs 800 g. in air and 600 g. in water. What is (\emph{a}) its volume? (\emph{b}) its sp. gr.? (\emph{c}) its density in the C. G. S. system?
5. What will be the weight (\emph{a}) of a cu. ft. 'of iron of sp. gr. 7? (\emph{b}) of a c.c.?
6. A block 7 X 7 X 3.5 cm. weighs 130 g. What is (\emph{a}) its density? (\emph{b}) its sp. gr.?
7. A piece of brimstone has a sp. gr. of 2.1. What will (\emph{a}) 2 c.c. of it weigh? (\emph{b}) 3 cu. ft.?
8. Eighty c.c. of a substance weighs 40 g. in water. What is its sp. gr.?
9. The weight of a given mass of substance is 660 g. ; its volume is 33 c.c. What is its sp. gr.?
10. A certain volume of sulphuric acid of density 1.84 weighs 82.8 g. The same volume of another liquid weighs 32 g. What is the density of this liquid?
11. A cube of iron 10 cm. on a side weighs 7500 g. (\emph{a}) What is its density? (\emph{b}) What will it weigh in alcohol of sp. gr. .92?
12. A cube 5 cm. on a side weighs 1.125 kg. in water. What is its sp. gr.?
13. A certain piece of brass loses 1250 g. in water. What is its weight?
14. How much will a kg. of iron weigh in sulphuric acid?
15. A rectangular block of stone measures 86 X 37 X 16 cm. and weighs 120 kg. Find its density.
16. A cubical block of wood 15 cm. on a side weighs 1 1 25 g. What is its density?
17. What is the sp. gr. of a piece of gold that weighs 2000 g. in air and 1890 g. in water?
18. What will be the volume of a brass 500 g. weight?
19. What is the volume of a block of platinum which weighs 41 g. in water?
20. What is the volume of a piece of metal which loses 40.36 g. in nitric acid?
21. What is the volume of a piece of platinum that weighs 650 g. in milk of sp. gr. 1.03?
22. Find the volume of a solid which weighs 20 g. in air and 15.65 g. in oil of turpentine.
23. A body weighs 540 g. in air and 240 g. in a liquid twice as dense as water. What is (\emph{a}) the volume of the body? (\emph{b}) the density?
24. What is the weight of a piece of metal of sp. gr. 8.9 that loses 51.1 g. in ether?
26. How much will a cu. ft. of lead weigh in oil of turpentine?
26. What is the weight (\emph{a}) in air and (\emph{b}) in alcohol of a copper rod 1 m. long and 2 cm. in diameter?
27. A block of tin weighs 347.5 g. What must be the sp. gr. of a liquid in which it will weigh 288 g.?
28. A piece of metal whose sp. gr. is 8 loses 224 g. in water. What is its (\emph{a}) weight? (\emph{b}) volume?
29. A piece of brass loses 25 g. in water. What will it weigh in sea- water of sp. gr. 1.026?
30. What will be the weight in ether of a cubical block 4 cm. on a side and of sp. gr. 1 .?
31. What will be the weight of a cubical block of iron 10 cm. on a side (\emph{a}) in water? (\emph{b}) in air? (\emph{c}) in sulphuric acid?
32. A body weighs 30 g. in air and 27 g. in water. What will it weigh in mercury?
33. What is the sp. gr. of a body which weighs 1200 g. in water and 1260 g. in another liquid whose sp. gr. is .8?
34. What must be the sp. gr. of a liquid in which a cu. ft. of coal weighs 35 lbs.?
35. What must be the area of cross-section of a tube 10 cm. long which shall hold 20 g. of alcohol?
36. How many g. of alcohol will a tube 5 cm. long and 4 cm. in diameter hold t
37. A piece of platinum loses 25 g. in sulphuric acid. What is its weight in air?
38. In a certain liquid a piece of metal loses 25 g. In water it loses 30 g. (\emph{a}) What is the volume of the metal? (\emph{b}) What is the sp. gr. of the first liquid?
39. An iron rod is 1 2 in. long, 4 in. wide, and 2 in. thick. What is its weight (\emph{a}) in water? (\emph{b}) in air?
40. How much will a loo-lb. iron weight weigh in sulphuric acid of sp. gr. 1.8 1
41. What is the weight of a zinc rod 2 m. long and 2 cm. in diameter (\emph{a}) in air? (\emph{b}) in ether?
42. A given bulk of lead weighs 250 g. How much will it weigh (\emph{a}) in hydrochloric acid 1 (\emph{b}) in kerosene?
43. What is the weight in copper sulphate solution of a mass of iron weighing 500 g. in air, if it loses 62.5 g. in water?
44. A certain substance of sp. gr. 12 weighs 60 g. in alcohol. What will be its weight in a liquid whose sp. gr. is 1.6 1
46. A piece of zinc weighs 40 g. in sulphuric acid. What will it weigh in oil of sp. gr. .65 1
46. How much will a brass kg. weight weigh in a liquid f as heavy as water?
47. The loss of weight of a piece of brass in a liquid of sp. gr. i§ is 50 g. What is (\emph{a}) its volume? (\emph{b}) its weight in air? (\emph{c}) its weight in water?
48. A piece of aluminum weighs 20.8 g. in air, 12.8 g., in water, and 15.28 g. in linseed oil. What is the sp. gr. (\emph{a}) of the aluminum? (\emph{b}) of the oil? (\emph{c}) What is the volume of the aluminum?
49. How much does a cubical block of wood, 4 cm. on a side and of sp. gr. .5, weigh in water 1 W'hat must be the sp. gr. of a liquid in which it will weigh 10 g.?
50. A piece of metal containing 8 cu. ft. weighs 3000 lbs. in water and 3100 lbs. in oil of turpentine of sp.gr. 0.8. What is (\emph{a}) its sp. gr.? (\emph{b}) its weight in air?
51. A body of sp. gr. 8.4 weighs 37 g. in water and 37.65 g. in oil of turpentine. What is the sp. gr. of the oil of turpentine?
52. Find the density of a body which weighs 63 g. in air and 37.5 g. in a liquid of density .85.
53. A body of sp. gr. 6 weighs 25 g. in water, 26.35 g- ^^ ether, and 24.81. g. in sea-water. Find the sp. gr. (\emph{a}) of the ether ; (\emph{d}) of the sea-water.
54. A certain volume of mercury weighs 216 g. and the same volume of another liquid weighs 14.8 g. Find the density of this liquid.
55. What is the sp. gr. of a liquid in which a body of sp. gr. II loses 50 g.? Its weight in water is 450 g.
56. A piece of metal weighs 20.4 g. in air, 14.4 g. in water, and 14.94 g. in linseed oil. What is the sp. gr. (\emph{a}) of the metal? (\emph{d}) of the oil? (\emph{c}) What is the volume of the metal?
57. A body of sp. gr. 2.5 weighs 31.25 lbs. in water. (\emph{a}) What is its volume? (\emph{b}) What does it weigh in air?
58. A lump of metal weighs a ton. Its weight in water is 1500 lbs. (\emph{a}) What is its sp. gr.? (\emph{b}) What would be its weight in a liquid whose sp. gr. is 1.75?
59. A solid of sp. gr. 4.5 loses 40 g. when weighed in water. What is (\emph{a}) its volume? (\emph{b}) its weight in water?
60. The weight of a given solid is 500 g. ; its weight in . water 450 g. ; and in nitric acid 439 g. What is the sp. gr. (\emph{a}) of the solid? (\emph{d}) of the nitric acid?
61. A given substance weighs 500 lbs. in air, loses 150 lbs. in water, and in a second liquid it weighs 240 lbs. What is the sp. gr. (\emph{a}) of the substance? (\emph{b}) of the second liquid?
62. A block of stone of sp. gr. 3.4 weighs 337.5 lbs. in a liquid 3 times as dense as water, and 212.5 ^^s. in another liquid, (\emph{a}) What is the sp. gr. of the second liquid.? (b) What is the volume of the block?
63. A diver with his suit on weighs 200 lbs. It takes * 3*5 of a cu. ft. of lead to just sink him. How many cu. ft. of water does he displace when in water?
64. A cube of pine 10 cm. on a side and of sp. gr. .5 has a hole 2 cm. in diameter and 5 cm. deep bored in the center of one face. The hole is filled with lead. How far will the cube sink in water?
65. A piece of silver when placed in alcohol is found to displace 9.6 g. When floated in mercury it displaces 9.25 c.c. What is (\emph{a}) the- weight of the silver? (\emph{b}) the volume? (c) the sp. gr.?
66. A liter flask ^^ full of water just sinks in water. What is the volume of the glass composing the flask? The sp. gr. of glass is 2.5.
67. If a pint of water weighed exactly a pound, how many cu. in. would it contain 1
68. A piece of wood containing 200 c.c. and of sp. gr. .5 is placed in a dish even full of water, (\emph{a}) How much water will be displaced 1 (\emph{b}) If it is placed in mercury, how many c.c. will be displaced? *
69. The pressure of the air will hold water 30 ft. high in a vacuum. How high will it hold mercury?
70. What is the volume of a solid weighing 25 g. in air and 20 g. in water? If placed in a dish of mercury, what per cent of its volume will be submerged?
71. Find the volume of a solid which weighs 20 g. iti air and 15.65 g. in oil of turpentine.
72. If the sp. gr. of air under ordinary conditions is .00129, and the sp. gr. of hydrogen .000105, what force will be needed to hold in place a balloon filled with hydrogen? The volume of the balloon is 125,000 c.c. and the weight of the balloon material is 100 g.
73. A body weighing 18 g. in air floats in water with \ of its volume submerged. How many grams must be placed upon it to just submerge it?
74. A cubical block 2 cm. on a side floats \ submerged in a liquid of sp. gr. 1.2. How much water will it displace if floating in water?
76. A cubical block 10 cm. on a side floats \ submerged in water, (\emph{a}) What will be the sp. gr. of a liquid in which it floats with twice as much of its volume submerged as would be submerged in a liquid of sp. gr. 1.5? (J?) What will be the volume submerged?
76. What is the sp. gr. of a liquid in which a solid will float with J as much of its volume submerged as would be submerged in alcohol of sp. gr. .8?
77. What proportional part of its volume will a wooden rod of sp. gr. .45 sink in alcohol?
78. To what depth will a block of stone of density 2.3 and cubical in form sink in mercury? Express your answer in terms of the edge of the cube.
79. If a body sinks J its volume in a liquid of sp. gr. .6, (\emph{a}) what part of its volume will it sink in a liquid of sp. gr. .2? (\emph{b}) What is thfe sp. gr. of the body?
80. A rod floats J submerged in alcohol. How much of the rod will be submerged in a liquid of sp. gr. .5?
81. A piece of cork floats on ether with 12 c.c. exposed. What is the entire volume of the cork?
82. A block weighing 40 g. in air floats in a liquid of sp. gr. .8 with J of its volume submerged. What is its cubical contents?
83. A uniform rod of sp. gr. .5 floats upright in alcohol with 10 cm. submerged. What is the length of the rod?
84. A rod 10 cm. long, composed of two substances whose sp. grs. are .5 and .9, respectively, floats § submerged in a liquid of sp. gr. 1.2. How much of each substance is in the rod?
86. There is a block of sp. gr. §. How much of it will be submerged when floated on a liquid whose sp. gr. is 4?
86. How much will a cu. dcm. of copper project above mercury when floated upon it?
87. A stick of wood 20 cm. long and 2 cm. square, of sp. gr. .5, has attached to one end a piece of metal also 2 cm. square and 1 cm. thick of sp. gr. 5.5. How much of the length of the stick will be out of water when floated in it?
88. If a uniformly dense block of wood weighs 30 lbs. per cu. ft., (\emph{a}) what is its sp. gr.? (\emph{b}) What part of its volume will project above alcohol if floated upon it?
89. A rod floats f submerged in a liquid of sp. gr. .8. How much of it will be submerged in a liquid of sp. gr. .6?
90. A body weighs 12 g. in air and floats with § of its volume submerged in water. How many g. must be placed upon it to just submerge it?
91. There is a block 10 cm. on a side which sinks \ of its volume in water and \ in another liquid, (\emph{a}) What is its sp. gr.? (\emph{b}) What is the sp. gr. of the other liquid t
92. How many cu. ft, of wood of sp. gr. .4 will be required to float in water 500 lbs. of iron, if the iron is entirely submerged?
93. How many c.c. of cork must be attached to lo c.c. of metal of sp. gr. 8, so that it will float in water entirely submerged?
94. How many grams of wood of sp. gr. .5 will a cubical block 10 cm. on a side, having a sp. gr. of 3.5, require to float it in alcohol when it is entirely submerged?
96. There is a uniform rod 6 ft. long and 4 in. square of sp. gr. .5. What must be the sp. gr. of a* cube of metal 4 in. on a side, which when attached to the lower end, will submerge the rod in water?
96. There is a wooden rod of sp. gr. .5, 2 cm. square, and 20 cm. long, floating upright in water. How many c.c. of lead must be attached to the lower end to submerge J of the rod?
97. How many grams of lead must be attached to a cu. dcm. of cork in order that it may just float in linseed oil.> "
98. The sp. gr. of a certain metal is 7. How much cork will it take to keep 100 lbs. of this metal so that it will just float in the water?
99. There is a metallic cubical box 10 cm. on a side, outside measure, which weighs 500 g. The bottom and sides are J cm. thick. It is filled with sulphuric acid of sp. gr. 1.8. How much wood, sp. gr. .4, must be attached to this so that it will sink J its volume in water?
100. If the sp.gr. of pure milk is 1.03, and an inspected sample has a sp. gr. of 1.02, what per cent of the sample is water?
101. How many cu. ft. of lead must be attached to the lower side of 10 cu. ft. of wood of sp. gr. .4 to just sink it in a liquid of sp.gr. 1.2?
102. A cubical block lo cm. on a side floats submerged J in a liquid of sp. gr. 1.2. How much lead must be attached to its lower side to just sink it?
103. How many c.c. of lead will a rod of wood 40 cm. long and 1 cm. square of sp. gr. .5 require to just submerge it when floating in alcohol?
104. A cubical block 10 cm. on a side floats \frac{}{} submerged in a liquid of sp. gr. 1.5. What must be the sp. gr. of a liquid in which it will float J submerged after 10 c.c. of lead are attached to its lower side?
106. The sp. gr. of a certain stick 25 cm. long and 2 cm. square is .4. How much iron 2 cm. square attached to one end will it take to sink it in water so that only 2 cm. will be above the surface?
106. A rod 10 cm. long and 10 sq. cm. in area of crosssection, sp. gr. .3, has attached to one end an iron ball 1.4 cm. in diameter ; when it is floated in brine, sp. gr. 1.3, how much of the rod will be above the brine?
107. What must be the sp. gr. of a liquid in order that a solid which sinks J its volume in ether may sink f of its volume?
108. What must be the sp. gr. of a liquid in which a body having a sp. gr. of 6.8 will float with J its volume submerged?
109. A body floats with J its bulk above water. What will be the sp. gr. of a liquid in which it will be half submerged?
110. What must be the sp. gr. of a liquid in which a solid which sinks \frac{}{} its volume in alcohol will sink \frac{}{} of its volume?
111. A body floats J submerged in a liquid of sp. gr. .8 and J submerged in another liquid. What is the sp. gr. of the second liquid?
112. A rod 30 cm. long and 1 cm. square, composed \frac{}{} of hard wood and \frac{}{} of soft wood, sinks 2 1 cm. in water. The sp. gr. of the soft wood is .4. What is the sp. gr. of the hard wood?
113. There is a rod 12 cm. long and 2 cm. square. Four cm. of length are of metal, the sp. gr. of which is 8, and the remainder of a metal whose sp. gr. is 10. How far will this rod sink in mercury?
114. A rod 12 cm. long and 1 cm. square sinks 10 cm. in alcohol. Half of its length is composed of wood of sp* gr. .3. What is the sp. gr. of the other half?
115. If the density of brass is 8.5, what will be the weight in air of a mass of brass which weighs in vacuo 500 g.? The weight of 1 liter of air is 1.2 g.
116. A flask which when filled with water weighs altogether 410 g. has 80 g. of a solid introduced, and being then filled with water weighs 470 g. What is the volume of a kilogram of the solid?
117. A dish containing several weights sinks in salt water to a certain mark, and when placed in fresh water and 104 g. are taken out it sinks to the same mark. What is the weight of both the dish and the weights left in it 1 The sp. gr. of salt water is 1.026.
118. A wooden rod of sp. gr. .3, 30 cm. long, has attached to one end a spherical ball of metal 4 cm. in diam-. eter and of sp. gr. 5. What must; be^ the area of cross-, section, of. the- rod^ so, that just \frac{}{} of its length shall be submerged, when ipamersed, in water?
119. A pubical block of wood: 2 cm. on a side weighs 5; g. How, far will it sink in alcohol of sp. gr. .8? 1/ 
120. A body weighing 20 g. in air is attached to a sinker which weighs 30 g. in water. Both together weigh 10 g. in water. What is the sp. gr. of the body?
121. What is the sp. gr. of a liquid in which the body mentioned in the last problem will float with § of its volume submerged?
122. A solid lighter than water and weighing 25 g. in air is fastened to a piece of metal and both together weigh 36 g. in water. If the piece of metal weighs 45 g. in water, what is the sp. gr. of the light solid?
123. A body weighing 20 g. in air is attached to 2 c.c. of a metal of sp. gr. 11. They both together weigh 15 g. in water. What is the sp. gr. of the body.?
124. The sp. gr. of a certain substance is 8. Ten c.c. of this substance are attached to a body which weighs 20 g. in air. Both together weigh 50 g. when submerged in water. What is the sp.gr. of the body?
125. A piece of wood weighs 8 g. in air, and when attached to a sinker which weighs 1 4.4 g. in turpentine they both, on being submerged in the turpentine, weigh 5 g. Find the sp. gr. of the wood.
126. A body weighs 20 g. in air and a sinker 30 g. in alcohol. They both weigh when submerged in alcohol 18 g. What is the sp. gr. of the body?
127. A body weighs 40 g. in air and a sinker 50 g. in a liquid of sp. gr. 1.4. They both together in this liquid weigh 20 g. Determine the volume and sp. gr. of the body.
128. A block weighing 10 g. in air and a sinker of sp. gr. II containing 2 c.c. are immersed in a liquid of sp. gr. 2. They weigh in this liquid 6 g. What is the sp. gr. of the block?
129. A liter flask weighs 25 g. When filled with a mixture of alcohol and water it weighs 867 g. How many c.c. of each in the flask?
130. A liter flask filled with mercury and water weighs 3570 g. (\emph{a}) How much mercury in the flask? (\emph{b}) How much water? The flask weighs 50 g.
131. A flask full of water weighs 500 g. When 120 g. of sand are put in and the water that overflows is allowed to run off, the flask is found to weigh 580 g. What is the sp. gr. of the sand? Disregard weight of flask.
132. There is a quart bottle half full of water and half full of another liquid. Liquids and bottle weigh 3 lbs. The bottle weighs \frac{}{} a lb. Find the sp. gr. of the second liquid.
133. A bottle when empty weighs 40 g., when full of mercury 543.2 g., and when 20 g. of mercury have been taken out and their place filled with another liquid it weighs 524.229 g. (\emph{a}) What is the volume of the bottle? (\emph{b}) What is the sp. gr. of the other liquid?
134. A bottle full of air weighs 625 g. When the air is partly exhausted it weighs 623.1 g. When the mouth is opened under water and the water allowed to take the place of the exhausted air, it weighs 2084.6 g. (\emph{a}) What is the sp. gr. of the air? (\emph{b}) How many c.c. of the air in the bottle were removed?
136. A certain vessel sinks to a mark in water, and after 10 g. are taken out it sinks to the same mark in a liquid of sp. gr. .6. What is the weight of the vessel and the contents?
136. A wooden vessel and load sinks to a certain mark in copper sulphate solution. On taking out 945 g. and placing in pure water it is found to sink to the same mark. What is the weight of both the vessel and the load it contained when in fresh water?
137. A weight of 25 g. is required to sink a Nicholson hydrometer to the mark. With a certain load on the pan it takes 17 g. to sink it. With the same load in the basket it takes 2 1 g. to sink it. What is the sp. gr. of the load?
138. It takes 45 g. to sink a Nicholson hydrometer to the mark. When a piece of quartz is placed upon the pan it takes 25 g. to sink it. When placed in the basket it takes 32.54 g. to sink it. What is the sp. gr. of the quartz?
139. A Fahrenheit hydrometer takes 62 g. to sink it to a certain mark on the stem when in water. It weighs 428 g. When placed in carbon di-sulphide it takes 140.4 g. to sink it to the same mark. What is the sp. gr. of the carbon di-sulphide?
140. A hydrometer sinks to a certain mark in a liquid of sp. gr. .6, but it takes 120 g. to sink it to the same mark in water. What is the weight of the hydrometer?
141. What volume of oak must be joined to 10 c.c. of flint glass in order that the sp. gr. of the whole may be 2?
142. Find the mean density of a substance composed of 8 parts by weight of a substance of density 4, and 12 parts of a substance of density 6.
143. Find the mean sp. gr. of a compound composed of 9 parts by volume of a substance of sp. gr. 7, and 6 parts of a substance of sp. gr. 3.
144. An alloy of gold and silver weighs 250 g. in air and 230.1 g. in water, (\emph{a}) How much of it is gold? (J?) How much silver?
145. The sp. gr. of two metals being 8 and 10, respectively, how much of each must be taken. to. mjike ipo g. off . alloy having the sp. gr.. of 9.4-?.
146. An alloy of goldand silver dis^pkces 25 g. of waten. An equal weight of silver displaces 35 g. (\emph{a}) What is its volume? (\emph{b}) How much gold. is. there? (\emph{c}) how much, silver?.
147. A bar supposed to be pure gold on being tested was found to contain some copper. It weighed 402.3 g. in water and 426.8 in air. (\emph{a}) How many c.c. of copper in it? (J?) How many c.c. of gold?
148. To a piece of nickel is attached a piece of silver weighing 20 g. Both together weigh 30 g. in water. What is (\emph{a}) the weight of the nickel? (\emph{b}) the volume?
149. A liter flask is filled with a mixture of two liquids of sp. gr. 1.4 together. The sp. gr. of one of the liquids is .8 and of the other 1.8. What volume of each enters into the mixture?
150. Equal volumes of three liquids are mixed together. The sp. gr. of two of them are .8 and .9, respectively, and the sp. gr. of the mixture is 1.2. What is the sp. gr. of the other liquid?
151. Two liters of a liquid of sp.gr. 1.22 are mixed with 3 liters of a liquid of sp. gr. 1.8. The mixture shrinks to 4.6 liters. What is its sp. gr.?
152. How many c.c. of a liquid of sp. gr. 1.4 must be mixed with 1 liter of a liquid of sp. gr. .8 to make a mixture of sp. gr. 1.2?
153. A solid of sp. gr. 1.5 floats with J its volume submerged on a mixture of equal parts water and another liquid. What is the sp. gr. of the second liquid?
154. A bottle when empty weighs 20 g.; when full of nitric acid it weighs 66.8 g., and when full of olive oil 47.45 g. What is the sp. gr. of the olive oil?
155. A certain bottle when full of ether weighs 194 g. How much will it weigh when full of sulphuric acid? The weight of the bottle is 50 g.
156. What is the diameter of a spherical ball that can be made from, a brass kg. weight?
167. Mercury is 13.6 as heavy as water. How much higher can water be raised in a perfect acting lifting pump on a day when the barometric pressure is 78 cm. than on a day when it is 74 cm.?
168. When the barometer stands at 760 mm. to what height can sulphuric acid of sp. gr. 1.8 be raised in a suction pump which is able to cause a barometer placed in a bell jar from which it exhausts the air to fall from 760 mm. to 20 mm.?
169. A cylindrical rod 3.5 m. long weighs 12.5 kg. in air and 2 kg. in water. Find radius and sp. gr.
160. The weight of a liter of hydrogen at 0° C. and 760 mm. pressure is .0896 g. Nitrogen is 14 times as heavy and oxygen 16 times as heavy as hydrogen. Air is composed of a mixture of 4 parts nitrogen and 1 part oxygen. What is the weight of a liter of air at the same temperature and pressure?
161. A d^tube is filled with water and glycerine unmixed. The height of the glycerine above the line of meeting is 70 cm. The height of the water on the other side of the tube above this line is 88.9 cm. What is the sp. gr. of the glycerine?
162. Two liquids in the opposite arms of a ^tube stand at 50 and 60 cm., respectively, above their point of junction. The sp. gr. of the first liquid is .8. What is the sp. gr. of the second?
163. Two vertical tubes have their upper ends connected by a Ktube and their lower ends in oil and sulphuric acid. The air is partly exhausted from the tube, and the oil is found to rise 80 cm. and the sulphuric acid 34.8. What is the sp. gr. of the oil?
164. A brass wire 7 m. long weighs in air 184.36 g. and in water 162.36 g. What is (\emph{a}) its volume? (\emph{b}) sp.gr.? (\emph{c}) radius?
166. There is a uniform glass tube 2 cm. in inside diameter and 20 cm. long. It weighs 50 g. From the center to one end it is filled with kerosene of sp. gr. .8, and the other end is filled with copper sulphate, of sp.gr. 1.2. Where will the rod balance?
166. A rod 20 cm. long and 1 cm. square has 5 cm. of its length composed of iron, 12 cm. of wood, of sp. gr. .5, and the remainder of lead. At what distance from the iron end is the center of gravity?
167. A ring containing a supposed diamond weighed 46.5 g. in air and 43.5 g. in water. The gold put into it weighed 45 g. The sp. gr. of the gold was 18 and the sp. gr. of a real diamond is 3.5. Was the stone a diamond?
168. A piece of silver weighing 20 g. and a piece of tin are fastened to the two ends of a string passing over a pulley and hang in equilibrium when immersed in water. Determine the weight of the tin.
169. Ten c.c. of silver are attached to one end of a string passing over a pulley. The silver is immersed in alcohol. How large a piece of brass attached to the other end of the string and immersed in water will just balance the silver?
170. A cube of platinum 2 cm. on a side attached to one arm of a balance is completely immersed in mercury. It is exactly counterbalanced by a sphere of lead attached to the other arm of the balance and completely immersed in water. What is the diameter of the sphere?
171. What will be the acceleration of a body of sp. gr. 5, when dropped into a liquid of sp. gr. 2? Neglect friction.
172. A liter flask filled with mercury weighs 14,000 g. When some of the mercury is poured out and water put in to take its place, the flask and contents weigh 12,740 g. (\emph{a}) What is the weight of the flask? (/;) How much water is put in?
173. A flask when filled with mercury weighs 4100 g. When J of the mercury is turned out and its place filled with a liquid of sp. gr. 1.6, it weighs 2900 g. Determine the weight and volume of the flask.
174. A cube of wood 10 cm. on a side, resting on the horizontal bottom of a dish, makes a perfectly tight contact but does not adhere. If water is poured on until the block is entirely covered, how much weight must be put upon the block to keep it from floating? The sp. gr. of the block is .5.
175. There is a rod 70 cm. long, 10 cm. square, of sp. gr. .5, that rests on the bottom of a vessel 50 cm. deep. What will be the tension on a string 10 cm. long, which is attached to the bottom of the vessel and to the lower end of the rod, when in the dish full of water?
176. A piece of wood of sp. gr. .4, 10 cm. long and 6 cm. /y square, is fastened to the bottom of a dish by a string attached to one end. If copper sulphate solution be poured in so as to cover the wood, what is the tension on the string?
177. A wooden sphere 10 cm. in diameter, and of sp. gr. .5, is attached by a string to the bottom of a dish and alcohol is poured on until the sphere is covered to a depth of 1 o cm. What is the tension on the string?
178. A block floats in water with \frac{}{} its volume submerged. How much of its volume will be under water when a liquid of sp. gr. .25 is poured on so as to cover the entire block?
179. A block floats \frac{}{} submerged in a liquid of sp. gr. 1.2, How much of it will remain in the liquid after another liquid of sp. gr. .4 is poured on until the block is covered?
180. A body floats f submerged in a liquid of sp. gr. 1.8. What is the sp. gr. of a liquid which, if turned on so as to entirely cover the body, will cause it to float with J its volume in each liquid?
181. A cubical block 10 cm. on a side, and of sp. gr. .5, is floating in water. Oil of sp. gr. .3 is poured on to the depth of 2 cm. How much of the block is above the oil?
182. In ^e previous problem how much oil must be poured on to bring the surface of the oil just on a level with the upper surface of the block?
183. A marble 2 cm. in diameter floats on mercury with J of its volume submerged. If oil of sp. gr. .8 be poured on until the marble is entirely covered, how much of it will be in mercury? How much additional pressure will it exert upon the bottom of the enclosing dish?
184. A liquid of sp. gr. .4 is poured upon a cubical block of wood 10 cm. on a side, floating J submerged.in water, until the top of the block is just even with the top of the liquid. What is now the lateral pressure on each of the sides of the block?