FORCE AND ACCELERATION
<i>g</i> = 32 ft. per sec. per sec, or 980 cm. per sec. per sec.
Wherever the pound is used as a unit of force, unless otherwise stated, it is to be considered equal to 32 poundals; similarly, the gram force equals 980 dynes.
1. What will be the velocity of a freely falling body at the end of the 5th second t How far will it travel in the 6th second? The body starts from rest.
2. A body acted upon by a constant force has an acceleration of 5 ft. per second per second, (\emph{a}) How far will it go in 8 seconds from rest.^^ (py What will be the distance traveled in the last 3 seconds .^^
3. How far will a body move along a frictionless horizontal plane in 5 seconds from rest if it has a constant acceleration of 3 ft. per second per second?
4. In the previous problem how far will the body travel in the last half of the 5th second?
5. A body falling 4 seconds passes over 750 ft. What was its initial velocity?
6. How much velocity must be given to a body shot vertically upward in order that at the end of the 3d second it shall have a velocity of 100 ft. per second?
7. A body is shot upward with a velocity of 400 ft. per second. What velocity will it have after 15 seconds.^
8. With how much vertical velocity must a bullet be shot into the air in order to fall back to its starting place in just 9 seconds after it left the gun?
9. In the previous problem, (\emph{a}) how far will the bullet travel? (\emph{d}) What will be the distances traveled in the 3d, 5th, and 9th seconds?
10. What initial velocity must a body have in order to V rise 500 ft. against gravity?
11. A body has fallen 1000 ft. What is its velocity?
12. With what downward velocity must a body be thrown from a tower 500 ft. high in order to reach the ground in 5 seconds?
13. A body falls 5 seconds. How far does it fall (\emph{a}) in the last half second? (\emph{b}) in the first half second?
14. A body is thrown downward from a tower 500 ft. high with a velocity of 50 ft. per second. How long will it take to reach the ground?
16. Two masses of 50 and 100 g., respectively, are pulled toward each other by a mutual attraction of 10 dynes. What will be the velocity of each at the end of 5 seconds?
16. A body is passing along a frictionless horizontal plane with a constant acceleration of 20 ft. per second per second. How far does it go in the first half of the 5th second from rest?
17. What is the attraction of gravity in a place where a body falls 6 ft. in the first second?
18. A body shot vertically into the air returns to its starting point in 7^ seconds, (\emph{a}) How far has it traveled? (\emph{b}) What was its initial velocity? (\emph{c}) How far did it travel in the 4th second?
19. A man is riding a bicycle at the rate of 15 miles an hour. How far will a package which he lets fall from a point 4 ft. above the ground move forward before striking the earth?
20. From the top of a 50-ft. mast in a ship sailing at the rate of 10 miles an hour a cannon ball is dropped. How V far back of the bottom of the mast will it strike the deck?
21. A body thrown vertically downward from the top of a tower with a velocity of 20 ft. per second strikes the ground after 6 seconds. How high is the tower?
22. With how much downward velocity must a body be thrown from a tower 800 ft. high in order to strike the ground in 3 seconds?
23. How long will it take a force of 10 units acting on a mass of 40 to change its velocity from 15 to 20?
24. A body starting from rest and acted upon by a constant force acquires a velocity of 400 cm. per second in going 1000 cm. What was the acceleration?
26. What must be the acceleration of a body to cause it to go 100 ft. in 5 seconds from rest?
26. A body moves 15 ft. in one second and 21 in the next. (\emph{a}) How long has it been moving with a uniform acceleration .? (J?) How far will it go in the next 3 seconds?
27. A body moves 20 ft. in one second and 28 in the next. (\emph{a}) How long has it been moving? (\emph{b}) What is its acceleration? (\emph{c}) How far will it go in the next 10 seconds?
28. A body weighing 5 lbs. and acted upon by a constant force moves 20 ft. along a frictionless horizontal plane in the 5th and 6th seconds from rest. What is the constant force "i
29. How long must a force of 10 poundals act on a mass of 30 lbs. to change its velocity from 5 to 25 ft. per second?
30. In what distance will a force of 4 poundals be able to stop a mass of 10 lbs. moving at the rate of 20 ft. per second?
31. How far will a mass of 6 lbs. move in 6 seconds when acted upon by a constant force of 20 poundals?
32. What force will move 10 lbs. 40 ft. from rest in 4 seconds?
33. How long must a force of 8 poundals act on a mass pAvy^J^ of 6 lbs. to change its velocity from 4 to 12 ft. per second?
34. In what distance will a force of 4 poundals be able to stop a mass of 20 lbs. moving at the rate of 40 ft. per second?
35. A body weighing 5 lbs. and moving 60 ft. per second encounters a constant resistance of 20 poundals. How far will it move before stopping t
36. What is the least force that will move 20 lbs. 50 ft. from rest in 5 seconds?
37. A mass of 30 g. is moving with a velocity of 12 cm. per second. How great a force will bring it to rest in 5 seconds?
38. A body starts along a frictionless horizontal plane with a velocity of 30 ft. per second and travels 100 ft., receiving a constant acceleration. At the end of the 100 ft. it is moving at the rate of 50 ft. per second, (\emph{a}) How long does it move? (\emph{b}) What is the constant acceleration?
39. Find the time and acceleration of a body whose velocity changes (\emph{a}) from 10 to 20 in going 100 ft.; (\emph{b}) from 15 to 5.
40. Two bodies are dropped from the same place J of a second apart. After how long a time will the distance between them be 33 m.?
41. Two bodies are dropped successively from the same point, and after the second has been falling 5 seconds, are 20 m. apart. What was the interval of time between tfieir release ^
42. The deck of a ship is 20 ft. above the water. With how much horizontal velocity must a cannon ball be shot in order to strike a body floating, just submerged, 1000 ft. away? The mouth of the cannon is at the level of the deck.
43. A cannon ball is fired from the top of a vertical cliff 800 ft. high with a horizontal velocity of 1000 ft. per second, (\emph{a}) How soon will it strike the level plain? (\emph{d}) How far from a point directly beneath the cannon will the ball strike?
44. In the previous problem how far from the mouth of the cannon would the ball strike the plain?
45. A stone is thrown from the top of a vertical cliff 40 ft. high with a horizontal velocity of 50 ft. per second. At what horizontal distance from the bottom of the cliff will it strike the ground?
46. A body shot from the top of a cliff with a horizontal velocity of 200 ft. per second strikes the ground at a horizontal distance of 1000 ft. from its starting point. How high is the cliff.?
47. The length of a frictionless inclined plane is 1000 ft. and its height 600 ft. (\emph{a}) How long will it take a body to slide down the plane? (\emph{d}) What will be its velocity at the bottom?
48. A body sliding down a frictionless inclined plane has at the end of the 3d second a velocity of 60 ft. per second. How far will it slide in 1 o seconds?
49. A body sliding down a frictionless inclined plane passes over 1 o ft. the first second. How far will it travel in 5 seconds?
50. A block is sliding down a frictionless inclined plane and at the end of 5 seconds is traveling 4 m. per second. What time will be required for it to travel 20 m. from the starting point?
51. With what velocity must a body be shot up a frictionless inclined plane which rises 3 ft. in 5, in order to ascend to a vertical height of 36 f t.?
52. A vessel sailing at the rate of 20 ft. per second is just passing a lighthouse, when a ball falls from a mast 100 ft. high. How far in front of the lighthouse will it strike the deck.?
53. A freely falling body passes the top of a tower 336 ft. high with a velocity of 64 ft. per second. It strikes the ground at the same instant that another body does, which started 3 seconds before it did. How far has the second body fallen?
54. A man standing on the edge of a cliff at the same instant shot a body vertically into the air and dropped another over the edge of the cliff. At the very instant the body shot into the air turns and begins to descend, the other strikes the ground. The distance between them at this instant is 1000 ft. What is the height of the cliff?
55. At the instant a body is dropped from the top of a tower 200 ft. high, another body is shot vertically into the air from the base of the tower, with a velocity of 200 ft. per second. How far above the bottom of the tower will they pass each other?
56. A ball is shot horizontally from the top of a vertical tower 480 ft. high with a velocity of 200 ft. per second ; at the same instant a stone is thrown vertically downward with a velocity of 32 ft. per second. They both strike the ground at the same instant, (\emph{a}) At what horizontal distance from the tower does the ball strike the ground? (\emph{b}) What is the elevation of the ground above that at the foot of the tower?
57. A ball is thrown vertically upward with a velocity of 100 ft. per second from a balloon which is sinking at the rate of 20 ft. per second. How far will the balloon be from the ball at the instant the ball begins to fall?
58. An elevator is descending at a uniform rate of 16 ft. per second when a bundle is knocked off and falls to the floor of the building 100 ft. below. How long is it falling?
59. What is the distance in the previous problem between the bundle and the elevator at the instant the bundle strikes the floor?
60. An elevator moving downward with a uniform velocity of 20 ft. per second loosens a nail from the wall of the elevator well as it passes. The nail begins to fall when it is at a distance of 10 ft. above the floor of the elevator. How long before it will pass this floor in its fall?
61. A force of 10 g. acting N. and another of 1000 dynes acting E. strike a ball weighing 100 g. What velocity will they give to the ball in 3 seconds?
62. A bucket weighing 20 lbs. is drawn up a well with a uniform acceleration of 5 ft. per second. What is the tension 6n the rope?
63. Attached to the ends of a rope passing over a frictionless pulley are two weights of 4 and 6 lbs., respectively. Supposing gravity alone acts on them, (\emph{a}) how fast will they move? (\emph{b}) in what direction?
64. A body of density 3 is dropped from the surface of the water. How long will it take it to sink to the bottom 500 ft. below? Neglect friction of water.
