COEFFICIENT OF FRICTION
1. A body is projected along a horizontal plane with a velocity of 100 ft. per second, coefficient of friction being T^. How far will it go before coming to rest?
2. A body is thrown on the ice with a velocity of 30 ft. per second. If the coefficient of friction between the body and the ice be ^, (\emph{a}) how soon will it stop? (\emph{b}) how far will it travel?
3. With what velocity must a body be moving in order, before coming to rest, to pass over 20 ft. on a horizontal plane, the coefficient of friction of which is \?
4. A body moves 10 ft. along a horizontal plane before coming to rest. The coefficient of friction is y\j. With what velocity must the body have started?
6. What is the coefficient of friction of a horizontal plane if a body shot with a velocity of 48 ft. per second moves 108 ft. before coming to rest?
6. A body moves with a velocity of 60 ft. per second along a horizontal plane, and is brought to rest after passing over 200 ft. of the plane. What is the coefficient of friction?
7. A body moving along a horizontal plane with a velocity of 100 ft. per second encounters a constant resistance equal to 1 of its weight. How far will it go before coming to rest?
8. What must be the coefficient of friction of a horizontal plane so that a body moving with a velocity of 30 ft. per second will come to rest after moving 1 00 ft. >
9. What is the coefficient of friction when a body moving along a horizontal plane with a velocity of 50 ft. per second comes to rest after moving 50 ft.?
10. A 4-lb. mass moving at the rate of 500 ft. per second is acted upon by a force which tends to stop it. The mass comes to rest after it has gone 25 ft. How large is this force?
11. A mass of 20 g. moving with a velocity of 50 cm. per second encounters a constant resistance of 10 dynes. How far will it move before coming to rest? How long will it move?
12. A body moving with a velocity of 50 ft. per second encounters a constant resistance which brings it to rest after it has passed over 25 ft. What is the ratio of resistance to the weight of the body?
13. A body moves along a frictionless horizontal plane with a velocity of 60 ft. per second. After traveling 200 ft. it comes to rest. What is, the ratio between its weight and the average resistance of the air?
14. A block, after sliding 25 ft. along a frictionless inclined plane which rises 3 ft. in 5, strikes a horizontal plane which has a coefficient of friction of J. How far will it move before coming to rest?
15. A body weighing lo lbs. is pushed 20 ft. along an inclined plane rising 3 ft. in 5. If the coefficient of friction between the block and plane is J, how much work has been done?
16. A body weighing 100 lbs. is pushed up an inclined plane 30 ft. high. The coefficient of friction is ^. How much work is done? The incline rises 6 ft. in 10.
17. A body slides down an inclined plane rising 3 ft. in 5. If the coefficient of friction is i, find the velocity gained in passing over 20 ft. of the plane.
18. How far will the body of the previous problem move if it passes onto a horizontal plane? Coefficient of friction is J.
19. A body moves 20 ft. along a horizontal plane whose coefficient of friction is ^, and then rises 10 ft. along a frictionless inclined plane rising 3 ft. in 5. Find the initial velocity.
20. If in the previous problem the body slides back down the inclined plane, how far will it move along the horizontal plane?
21. What must be the coefficient of friction on an inclined plane rising 1 ft. in 4, so that it shall take 100 ft. lbs. of work to raise an 8-lb. mass 10 ft. vertically?
22. With what velocity must a body weighing 10 lbs. be started in order to move 50 ft. along a horizontal plane having a coefficient of friction of J? With what energy must it start?
23. A body sliding 20 ft. along a rough inclined plane descends vertically 16 ft. If the coefficient of friction between the block and the plane is i, what velocity will the body acquire?
24. A boy capable of exerting a force of 20 lbs. wishes to raise a mass of 50 lbs. to a height of 4 ft. What is the shortest frictionless plank that he can use as an inclined plane to do this? If coefficient of friction equals ^, how much aid will he require to do it.**
25. In the previous problem how much work will he do? How much work will his helper do?
26. If a mass of 1 mgm. resting on a horizontal plane is acted on by a force of 1 dyne for 10 seconds, what velocity will the mass acquire in the time if coefficient of friction is i?
27. What will be the kinetic energy of the mass of the previous problem and how far will it move in the 1 o seconds?
28. A mass of 1000 lbs. rests on an incline. How much work must be done in drawing the body 20 ft. up the incline if the projection of the incline on the horizontal is 16 ft. and the coefficient of friction J?
29. A pair of horses capable of pulling with a force of 4000 lbs. are attached to a loaded dray which weighs 10 tons. If the coefficient of friction is y*^, how steep an incline can they ascend?
30. A body sliding down a rough inclined plane travels 10 ft. along the plane, but descends only 6 ft. vertically. If the force of friction is equal to 1 the weight of the body, find the velocity gained during the descent.
31. A block weighing 50 lbs. rests on an incline such that the block must move 5 ft. to rise 3 ft. The coefficient of friction is .25. How much work must be done by a force parallel to the incline in drawing the block 30 ft.?
32. A 5-lb. weight hanging over the edge of a table drags a lo-lb. weight along the table. The coefficient of friction is ^. How fast does the weight move?
33. A 5-lb. weight hanging over the edge of a table drags a 2 5-lb. weight along it. If the coefficient of friction between the table and the 2 5-lb. weight is j*^, find the acceleration.
34. A mass of 10 lbs. rests upon a table; the coefficient of friction is f . It is acted upon by a 5-lb. weight hanging over the edge of the table. Find the distance passed over by the weight in 1 second.
36. A boat weighing 2 tons is moving at the rate of 10 miles per hour when the engine breaks. If the average coefficient of resistance of the water is ^, how far will the boat go before it stops?